TBD

### 2021-02-20 outputs/paper/paper.Rmd
typos + altered t-test graph
next steps: chi-square results formatting.

In terms of effects on revenue and/or overall sales for restaurants during the intervention period, Figure 5 shows us that more restaurants within the treatment group saw decreases in revenue compared to the prior quarter (July 1 - Sep 30), while the control group's revenue largely remained the same. In addition to this, Figure 6 shows that of those restaurants that saw a decrease in revenue, the treatment group saw the harshest declines in revenue during the intervention period. A Chi-Square test for whether the restaurant saw a decrease in revenue showed that restaurants in the treatment group were more likely to report a decrease in revenue *X*^1 (2, *N* = 330) = 220.73, *p* < 2.2e-16. The percentage decrease in revenues also showed a significant relationship, where restaurants in the treatment group are most likely to report higher loss of revenue during the intervention period *X*^2 (3, *N* = 330) = 178.33, *p* < 2.2e-16. Prior to the intervention period, it appears as though both groups had similar breakdowns of revenue coming from take-out and/or delivery (Figure 7).

@@

#Q5 + Q6 compiled t-test table
t_tests <- map_df(list(t3, t4), tidy)
t_tests = subset(t_tests, select = -c(alternative, method))
t_tests %>%  
  kable(
    col.names = c("Mean of the Differences",
                  "Mean (Employees Before Intervention)",
                  "Mean (Employees Post-Intervention)",
                  "t",
                  "p",
                  "df",
                  "Low",
                  "High")

  ) %>%
  add_header_above(c(" ", "Control" = 1, "Treated" = 1, " ", " ", " ", "Confidence" = 2)) %>%
  kable_paper(c("striped", "hover")) %>%
  landscape()

>>>>

In terms of effects on revenue and/or overall sales for restaurants during the intervention period, Figure 5 shows us that more restaurants within the treatment group saw decreases in revenue compared to the prior quarter (July 1 - Sep 30), while the control group's revenue largely remained the same. In addition to this, Figure 6 shows that of those restaurants that saw a decrease in revenue, the treatment group saw the harshest declines in revenue during the intervention period. A Chi-Square test for whether the restaurant saw a decrease in revenue showed that restaurants in the treatment group were more likely to report a decrease in revenue *X*^2 (2, *N* = 330) = 220.73, *p* < 2.2e-16. The percentage decrease in revenues also showed a significant relationship, where restaurants in the treatment group are most likely to report higher loss of revenue during the intervention period *X*^2 (3, *N* = 330) = 178.33, *p* < 2.2e-16. Prior to the intervention period, it appears as though both groups had similar breakdowns of revenue coming from take-out and/or delivery (Figure 7).

@@

#Q5 + Q6 compiled t-test table
t_tests <- map_df(list(t3, t4), tidy)
t_tests = subset(t_tests, select = -c(alternative, method, conf.low, conf.high))
t_tests %>%  
  kable(
    col.names = c("Mean of the Differences",
                  "Mean (Employees Before Intervention)",
                  "Mean (Employees Post-Intervention)",
                  "t",
                  "p",
                  "df")

  ) %>%
  add_header_above(c(" ", "Control" = 1, "Treated" = 1, " ", " ", " ")) %>%
  kable_paper(c("striped", "hover")) %>%
  landscape()
